### 2020-07-10 tex_files/artificial_data.tex
Added PRH class

with $L$ being a lower triangular matrix called the \emph{Cholesky factor} of $C$. We can show that there is a relation between the CHolseky and eigenvalue factorizations of a given matrix. First observe that, from the eigenvalue decomposition:

@@

But now we can rerite the \eqref{eq:eigen-cov-decomp} as

@@

>>>>

with $L$ being a lower triangular matrix called the \emph{Cholesky factor} of $C$. We can show that there is a relation between the Cholesky and eigenvalue factorizations of a given matrix. First observe that, from the eigenvalue decomposition:

@@

But now we can rewrite the \eqref{eq:eigen-cov-decomp} as

@@

For what regards the noise, in ref \cite{Press1992} they identify the expectation value $\langle n_i^2 \rangle$ with the square of the quoted error on the magnitude. This makes sense if one assumes that $n_i$ is a random gaussian number with zero mean and variance given by the experimental error. So

\begin{equation}
\langle n_i^2 \rangle = e_i^2
\end{equation}

Then our prescription to generate the dataset becomes

\begin{align}\label{eq:reform-artificial-prescr}
y_i = \sum_{j=1}^{2N} L_{ij} r_j + e_i r_i, \quad i = 1, \dots , 2N
\end{align}

where $L$ is the lower triangular Cholesky factor of the estimated covariance $C$, i.e.

\[
C = L L^{\dagger}
\]

We interpret the first $N$ points $y_1, \dots, y_N$ as measurement of a mock light curve at times $t_1, \dots , t_N$, 
while the other $N$ points $y_{N+1}, \dots, y_{2N}$ are measurements of the \emph{same} mock curve (apart from noise) at times 
$t_1-\Delta t, \dots , t_N-\Delta t$, where the true delay can be decided \emph{a priori} when building the covariance. Therefore, if we assign each point of the second curve at times $t_1, \dots , t_N$ it will exactly experience a delay $\Delta t$.

In figure \ref{fig:artif-dataset-5-vs-real} we see a mock light curve compared to the true light curve from which it has been generated. Both the curves have been scaled to have zero mean and unit variance, in order to make a direct comparison. In figure \ref{fig:artif-dataset-5-shift-comparison} we can see a comparison between the mock curves of the same mock dataset, with a relative time delay of about $18$ days.

\begin{figure}
\centering
\includegraphics[scale=0.45]{realiz5_comparison.pdf}
\caption{Realization 5 vs true quasar data, image A.}
\label{fig:artif-dataset-5-vs-real}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.45]{Montecarlo_y_vs_y_delayed.pdf}
\caption{Realization 5: mock light curve vs its shifted version, with a true delay of about $18$ days.}
\label{fig:artif-dataset-5-shift-comparison}
\end{figure}
